Postural developments mediate children's visual access to social information

### 2018-01-30 writeup-cogsci/cogsci2018_faceOnly_alessandro.Rmd

However, as children are learning from others around them, their view of the world is also radically changing  [@adolph2007]. Infants' motor abilities improve dramatically near the end of the first year of life, allowing them to locomote independently. These motor changes have significant consequences for what children see; crawling and walking infants simply have different views of the world. For example, during spontaneous play in a laboratory playroom, toddlers are more likely to look at the floor while crawling than while walking [@franchak2011]; in general, walking infants tend to have full visual access to their environment and the people in it, while crawling infants do not [@kretch2014].

@@

## Head-mounted camera
```{r headcam, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.label="headcam", fig.cap = "Field of view for two different headcam configurations (we used the one below in our current study)."}
img <- png::readPNG("images/viewangle_cut.png")
grid::grid.raster(img)
```

>>>>

However, as children are learning from others around them, their view of the world is also radically changing  [@adolph2007]. Infants' motor abilities improve dramatically near the end of the first year of life, allowing them to locomote independently. These motor changes have significant consequences for what children see; crawling and walking infants simply have different views of the world. For example, during spontaneous play in a laboratory playroom, toddlers are more likely to look at the floor while crawling than while walking [@franchak2011head]; in general, walking infants tend to have full visual access to their environment and the people in it, while crawling infants do not [@kretch2014].

@@

## Head-mounted camera
```{r headcam, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.label="headcam", fig.cap = "Field of view for two different headcam configurations (we used the lower in our current study)."}
img <- png::readPNG("images/viewangle_cut.png")
grid::grid.raster(img)
```

### 2018-01-30 writeup-cogsci/cogsci2018_faceOnly_alessandro.tex

\author{{\large \bf Alessandro Sanchez} \\ \texttt{sanchez7@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Bria Long} \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Ally Kraus} \\ \texttt{allison.m.kraus@gmail.com} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

\begin{abstract}
The ability to process social cues--including eye gaze--is a critical
component of children's early language and cognitive development.
However, as children reach their first birthday, they begin to locomote
themselves, walking and exploring their visual environment in an
entirely new way. How do these postural and locomotive changes affect
children's access to the social information relevant for word-learning?
Here, we explore this question by using head-mounted cameras to record
infants' (8-16 months of age) egocentric visual perspective and use
computer vision algorithms to detect the proportion of faces and wrists
in infants' environments. We find that infants' posture and orientation
to their caregiver largely mediates their access to social information,
suggesting that postural and locomotive developments play a significant
role in the emergence of children's linguistic and social capacities.
Broadly, we suggest that the combined use of head-mounted cameras and
the application of new computer vision techniques is a promising avenue
for understanding the statistics of infants' visual and linguistic
experience.

@@

However, as children are learning from others around them, their view of
the world is also radically changing (K. Adolph \& Berger, 2007).
Infants' motor abilities improve dramatically near the end of the first
year of life, allowing them to locomote independently. These motor
changes have significant consequences for what children see; crawling
and walking infants simply have different views of the world. For
example, during spontaneous play in a laboratory playroom, toddlers are
more likely to look at the floor while crawling than while walking (J.
Franchak, Kretch, Soska, \& Adolph, 2011); in general, walking infants
tend to have full visual access to their environment and the people in
it, while crawling infants do not (K. S. Kretch, Franchak, \& Adolph,
2014).

@@

Recent technological developments allow for testing of this hypothesis
by documenting the experiences of infants and children from their own
perspective. By using head-mounted cameras, researchers have begun to
record the visual experiences of infants and children-- which even for
walking children are extremely different from the adult perspective (and
not easily predicted by our own adult intuitions) (Clerkin, Hart, Rehg,
Yu, \& Smith, 2017; J. Franchak et al., 2011; Yoshida \& Smith, 2008).
While children's views tend to be more restricted and dominated by
objects and hands (Yoshida \& Smith, 2008), both computational and
empirical work suggest that this restricted viewpoint may be more
effective for learning objects and their labels than the comparable
adult perspective (Bambach, Crandall, Smith, \& Yu, 2017; D. Yurovsky,
Smith, \& Yu, in press). Further, recent work also suggests dramatic
changes in the child's perspective over the first two years of life, as
views transition from primarily containing close up views of faces to
capturing views of hands paired with the objects they are acting on
(Fausey, Jayaraman, \& Smith, 2016).

@@

\hypertarget{ref-franchak2011}{}
Franchak, J., Kretch, K., Soska, K., \& Adolph, K. (2011). Head-mounted
eye tracking: A new method to describe infant looking. \emph{Child
Development}.

>>>>

\author{{\large \bf Alessandro Sanchez} \\ \texttt{sanchez7@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Bria Long} \\ \texttt{bria@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Allison M. Kraus} \\ \texttt{allison.m.kraus@gmail.com} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

@@

\begin{abstract}
The ability to process social information--including eye gaze--is a
critical component of children's early language and cognitive
development. However, as children reach their first birthday, they begin
to locomote themselves, walking and exploring their visual environment
in an entirely new way. How do these postural and locomotive changes
affect children's access to the social information relevant for
word-learning? Here, we explore this question by using head-mounted
cameras to record infants' (8-16 months of age) egocentric visual
perspective and use computer vision algorithms to detect the proportion
of faces and wrists in infants' environments. We find that infants'
posture and orientation to their caregiver largely mediates their access
to social information, suggesting that postural and locomotive
developments play a significant role in the emergence of children's
linguistic and social capacities. Broadly, we suggest that the combined
use of head-mounted cameras and the application of new computer vision
techniques is a promising avenue for understanding the statistics of
infants' visual and linguistic experience.

@@

However, as children are learning from others around them, their view of
the world is also radically changing (K. Adolph \& Berger, 2007).
Infants' motor abilities improve dramatically near the end of the first
year of life, allowing them to locomote independently. These motor
changes have significant consequences for what children see; crawling
and walking infants simply have different views of the world. For
example, during spontaneous play in a laboratory playroom, toddlers are
more likely to look at the floor while crawling than while walking
(Franchak, Kretch, Soska, \& Adolph, 2011); in general, walking infants
tend to have full visual access to their environment and the people in
it, while crawling infants do not (Kretch, Franchak, \& Adolph, 2014).

@@

Recent technological developments allow for testing of this hypothesis
by documenting the experiences of infants and children from their own
perspective. By using head-mounted cameras, researchers have begun to
record the visual experiences of infants and children-- which even for
walking children are extremely different from the adult perspective (and
not easily predicted by our own adult intuitions) ({\textbf{???}};
Clerkin, Hart, Rehg, Yu, \& Smith, 2017; Yoshida \& Smith, 2008). While
children's views tend to be more restricted and dominated by objects and
hands (Yoshida \& Smith, 2008), both computational and empirical work
suggest that this restricted viewpoint may be more effective for
learning objects and their labels than the comparable adult perspective
(Bambach, Crandall, Smith, \& Yu, 2017; D. Yurovsky, Smith, \& Yu, in
press). Further, recent work also suggests dramatic changes in the
child's perspective over the first two years of life, as views
transition from primarily containing close up views of faces to
capturing views of hands paired with the objects they are acting on
(Fausey, Jayaraman, \& Smith, 2016).

@@

\hypertarget{ref-franchak2011head}{}
Franchak, J. M., Kretch, K. S., Soska, K. C., \& Adolph, K. E. (2011).
Head-mounted eye tracking: A new method to describe infant looking.
\emph{Child Development}, \emph{82}(6), 1738--1750.
